---
title: "Gene List to BED"
output: html_notebook
---

```{r}
coord <- read.table("genes_mm39.txt",header = T,sep = "\t")

gl.DKOspec <- read.table("1.list_genes_names_lncRNA_RNAseq_DKOspec.txt")[,1]
gl.common <- read.table("2.list_genes_names_lncRNA_RNAseq_NonChangedDKOvsWT.txt")[,1]
gl.DKOup <- read.table("3.list_genes_names_lncRNA_RNAseq_UpregulatedDKOvsWT.txt")[,1]
```

```{r}
match<-coord[coord$Gene.name %in% gl.DKOspec,]

bed.DKOspec <- data.frame( chr=paste0("chr",match$Chromosome.scaffold.name), 
                           start=match$Transcript.start..bp., 
                           end=match$Transcript.end..bp., 
                           name=match$Gene.name, 
                           score=0, 
                           strand=gsub("1","+",gsub("-1","-",match$Strand)))
                        
write.table(bed.DKOspec, file="lncRNA_DKOspec.bed",col.names = F,row.names = F, quote = F, sep = "\t")
```

```{r}
match<-coord[coord$Gene.name %in% gl.common,]

bed.common <- data.frame( chr=paste0("chr",match$Chromosome.scaffold.name), 
                           start=match$Transcript.start..bp., 
                           end=match$Transcript.end..bp., 
                           name=match$Gene.name, 
                           score=0, 
                           strand=gsub("1","+",gsub("-1","-",match$Strand)))
                        
write.table(bed.common, file="lncRNA_common.bed",col.names = F,row.names = F, quote = F, sep = "\t")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

```{r}

match<-coord[coord$Gene.name %in% gl.DKOup,]

bed.DKOup <- data.frame( chr=paste0("chr",match$Chromosome.scaffold.name), 
                           start=match$Transcript.start..bp., 
                           end=match$Transcript.end..bp., 
                           name=match$Gene.name, 
                           score=0, 
                           strand=gsub("1","+",gsub("-1","-",match$Strand)))
                        
write.table(bed.DKOup, file="lncRNA_DKOup.bed",col.names = F,row.names = F, quote = F, sep = "\t")
```
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

